Response to reviewers

### 2025-08-06 paper_plos/reviewer_respose_letter_V1.qmd
small edits to the response letter

Also, the double constraint ends up fixomg the aggregated zonal value to match the 'mass' at the zone itself (i.e., reproducing what we already imposed onto the model). In this way, the $ij$ flows are the only useful thing for analysis. This focus has not tradtionally occupied the research context of accessibility-based work.

@@

Thank you for this comment. The historical literature review section (Accessibility and spatial interaction modelling: two divergent research streams) covers upward of 76 papers citing Wilson and Hansen, condensed into about 3 pages. This section sets the stage by outlining Wilson’s balancing factors and highlighting how place-based accessibility literature (largely based on Hansen-type measures) has not adopted these balancing factors. This context is needed for the subsequent, more detailed 16-page section, which introduces the newly proposed family of accessibility measures which incorporate Wilson's balancing factors. We believe this structure balances breadth and depth appropriately--we've tried to reduce redundancies and improve when possible. We hope you find the revised manuscript easier to follow.

@@

However, we do acknowledge some utility-based approaches within the spatial interaction literature--for example, "The third subset of the spatial-interaction focused literature, depart from Hansen's [@hansen1959] definition, aligning instead with microeconomic or utility-based interpretations of potential spatial interaction e.g., [@morrisAccessibilityIndicatorsTransport1979; @leonardiRandomUtilityDemand1984]."

>>>>

@@

Thank you for this comment. The historical literature review section (Accessibility and spatial interaction modelling: two divergent research streams) covers upward of 76 papers citing Wilson and Hansen, condensed into about 3 pages. This section sets the stage by outlining Wilson’s balancing factors and highlighting how place-based accessibility literature (largely based on Hansen-type measures) has not adopted these balancing factors. This context is needed for the subsequent, more detailed 16-page section, which introduces the newly proposed family of accessibility measures which incorporate Wilson's balancing factors. We believe this structure balances breadth and depth appropriately; we've tried to reduce redundancies and improve when possible. We hope you find the revised manuscript easier to follow.

@@

However, we do acknowledge some utility-based approaches within the spatial interaction literature. For example, "The third subset of the spatial-interaction focused literature, depart from Hansen's [@hansen1959] definition, aligning instead with microeconomic or utility-based interpretations of potential spatial interaction e.g., [@morrisAccessibilityIndicatorsTransport1979; @leonardiRandomUtilityDemand1984]."
